---
title: "Farmers hold diverse and connected values towards crops"
author: "Marilou Demongeot, Antoine Doncieux, Tatiana Cardenas, Anna Porcuna-Ferrer, Yildiz Aumeeruddy-Thomas, Sophie Caillon, Jonathan Locqueville, Doyle McKey, Victoria Reyes-García, Delphine Renard"
date: '2025-12-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6, cache.lazy = FALSE, cache = FALSE)

```


# Packages loading

```{r load_packages, include=FALSE,echo=FALSE}

library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
library(conflicted)
library(stringr)
library(CooccurrenceAffinity)
library(igraph)
library(DHARMa)
library(sf)
library(MASS)
library(broom.mixed)
library(lemon)
library(circlize)


## Conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("arrange", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("degree", "igraph")

# Cleaning the workspace
rm(list=ls())
set.seed(100)

# data repository
setwd(rstudioapi::getActiveDocumentContext()$path %>% dirname()) 
getwd()
```


# Loading dataset

```{r loading dataset , include=FALSE,echo=FALSE}

df_articles = read_xlsx("df_crops_values_review.xlsx", sheet = "df_articles")

df_crops_values = read_xlsx("df_crops_values_review.xlsx", sheet = "df_values_crops")

df_tree_values = read_xlsx("df_crops_values_review.xlsx", sheet = "df_tree_of_values")

df_models = read_xlsx("df_crops_values_review.xlsx", sheet = "df_models")

df_drivers = read_xlsx("df_crops_values_review.xlsx", sheet = "df_externals_drivers")
```


# Descriptive analysis of the studies reviewed
```{r descriptive of paper content , include=FALSE,echo=FALSE}

# Number of studies reviewed
length(unique(df_articles$Paper_ID))

# Subsistance / local market ; global market (% of studies)
market = df_articles %>%
  filter(!integration_to_market_recode == "NA") %>%
  group_by(integration_to_market_recode) %>% 
  mutate(Nbr_studies = length(Paper_ID)*100/92) %>%
  distinct(integration_to_market_recode, Nbr_studies)

# Number of species 
df_crops_values_nbr = df_crops_values %>%
  filter(!Crop_name %in% c("NR", "NA"))
length(unique(df_crops_values_nbr$Crop_name)) # 135 species


# Number of cereal crops 
df_crops_values_cereal = df_crops_values %>%
  filter(Crop_class == "Cereals")
length(unique(df_crops_values_cereal$Crop_name)) # 16 species
length(unique(df_crops_values_cereal$Paper_ID)) 
52*100/125 # 42% of studies

# Proportion of articles with values attributed to each crop class (e.g., cereals, nuts)
Tree_df = df_crops_values %>%
  select(Paper_ID,Crop_class) %>%
  group_by(Crop_class) %>%
  mutate(Proportion_crops = length(unique(Paper_ID))*100/125) %>%
  distinct(Crop_class,Proportion_crops)

# Number of crops species evaluated at the varietal/landrace level

df_crops_values_varietal = df_crops_values %>%
  filter(Crop_level == "landrace/variety")
length(unique(df_crops_values_varietal$Crop_name)) #32 varieties


```

## Mapping the studies (Figure 1)

```{r map of the studies , include=FALSE,echo=FALSE}

Paper_contry = df_articles %>%
  mutate(WB_NAME  = country ) %>%
  separate(col=WB_NAME, into = paste0("WB_NAME_sup", 1:15), sep=";") %>% 
  select(Paper_ID, matches("WB_NAME")) %>%
  pivot_longer(cols = c(2:16)) %>%
  drop_na() %>%
  rename(WB_NAME = value) %>%
  select(Paper_ID,WB_NAME) %>%
  mutate(WB_NAME = str_replace_all(WB_NAME, pattern=" ", repl=""), 
         WB_NAME = recode(WB_NAME, 
                          "USA" = "UnitedStatesofAmerica",
                          "United-States" = "UnitedStatesofAmerica",
                          "Coted'Ivoire" = "IvoryCoast",
                          "ElSavador" = "ElSalvador",
                          "Tanzania" = "UnitedRepublicofTanzania",
                          "Congo" = "DemocraticRepublicoftheCongo",
                          "Gana" ="Ghana",
                          "Scotland" = "UnitedKingdom")) %>% 
  group_by(WB_NAME) %>%
  mutate(Nbr_etude= length(unique(Paper_ID)),
         Reviewed = "Yes") %>%
  distinct(WB_NAME,Nbr_etude,Reviewed) 

length(Paper_contry$WB_NAME) # 67 countries within the 125 studies


# World map 

sf_World_plot <- st_read("ne_110m_admin_0_sovereignty.shp", stringsAsFactors = FALSE) %>%
  select(SOVEREIGNT, CONTINENT) %>%
  rename(WB_NAME = SOVEREIGNT) %>%
  st_transform("ESRI:54030") %>% # Robinson projection
  mutate(WB_NAME = str_replace_all(WB_NAME, pattern=" ", repl="")) 

# Calcule le centre des pays ou y'a eu des publis
sf_World_final = sf_World_plot %>%
  full_join(Paper_contry)%>% 
  st_transform("ESRI:54030") %>%
  mutate(Centroid = st_centroid(geometry)) %>%
  mutate(x = as.numeric(st_coordinates(Centroid)[,1]),
         y = as.numeric(st_coordinates(Centroid)[,2])) %>% 
  st_as_sf(coords = c("x", "y"), st_crs("ESRI:54030"), remove=TRUE) %>% # Robinson projection
  filter(Reviewed == "Yes") %>%
  as.data.frame()


# Map
ggplot(data = sf_World_plot) +
  geom_sf(color = "darkgray", fill = "lightgray") +
  coord_sf(crs = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 
            +datum=WGS84 +units=m +no_defs", expand = F) +
  theme_bw() +
  theme(panel.grid.major = element_line(color = 'white', 
                                        size = 0, 
                                        linetype = "solid"),
        panel.border = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position = "none") + 
  geom_point(aes(x=x,y=y),sf_World_final,size=sf_World_final$Nbr_etude/3,alpha=0.8,colour="black") +
  xlab("") + ylab("")



```


# Proportion of values within each domain and levels

```{r Values proportion , include=FALSE,echo=FALSE}

# Proportion of values per domain 

df_crops_values_prop = df_crops_values %>%
  group_by(Domain) %>%
  mutate(Number_of_domain_value = length(Level_1)) %>%
  distinct(Number_of_domain_value,Domain ) %>%
  mutate(Number_of_domain_value_prop = Number_of_domain_value*100/1716)


### Domain 3. Rural economy

##### Level 1 #####
df_crops_values_prop_economy = df_crops_values %>%
  filter(Domain == "3. Socio-economic") %>%
  group_by(Level_1) %>%
  mutate(Number_of_L1_value = length(Level_1)) %>%
  distinct(Number_of_L1_value,Level_1 ) %>%
  mutate(Number_of_L1_value_prop = Number_of_L1_value*100/741)

#### Level 2 ####
df_crops_values_prop_economy_L2 = df_crops_values %>%
  filter(Domain == "3. Socio-economic") %>%
  group_by(Level_2) %>%
  mutate(Number_of_L2_value = length(Level_2)) %>%
  distinct(Number_of_L2_value,Level_2 ) %>%
  mutate(Number_of_L2_value_prop = Number_of_L2_value*100/741)


### Domain 6. Agroecological traits  

##### Level 1 #####

df_crops_values_prop_AT = df_crops_values %>%
  filter(Domain == "6. Agroecological traits") %>%
  group_by(Level_1) %>%
  mutate(Number_of_L1_value = length(Level_1)) %>%
  distinct(Number_of_L1_value,Level_1 ) %>%
  mutate(Number_of_L1_value_prop = Number_of_L1_value*100/442)

#### Level 2 ####
df_crops_values_propagroeco_L2 = df_crops_values %>%
  filter(Domain == "6. Agroecological traits") %>%
  group_by(Level_2) %>%
  mutate(Number_of_L2_value = length(Level_2)) %>%
  distinct(Number_of_L2_value,Level_2 ) %>%
  mutate(Number_of_L2_value_prop = Number_of_L2_value*100/442)


```


## Values as priority

```{r Values priority  , include=FALSE,echo=FALSE}

paper_priority = df_crops_values %>%
  filter(!Ranking =="NA")
length(unique(paper_priority$Paper_ID)) # 61*100/125 = 49%

  
values_priority = df_crops_values %>%
  filter(!Ranking =="NA") %>%
    filter(Ranking %in% c("most important", "important")) %>%
  mutate(Ranking_important = recode(Ranking,
                                   "most important" = "priority",
                                   "important" = "priority")) %>%
  distinct(Level_1, Paper_ID, Ranking_important) %>%
  group_by(Level_1, Ranking_important) %>%
  mutate(values_priority = length(unique(Paper_ID))) %>%
  distinct(Ranking_important,values_priority) 

34*100/61  # 56% of 3.3. yield were mentionned as a priority
31*100/61 # 51% of 3.2 monetary value were mentionned as a priority

print(" we recoded the ranking 'most important' and 'important' as one unique category to overcome the multiple citations of values per crops and papers")


values_priority = df_crops_values %>%
  filter(!Ranking =="NA") %>%
    filter(Ranking %in% c("most important", "important")) %>%
  mutate(Ranking_important = recode(Ranking,
                                   "most important" = "priority",
                                   "important" = "priority")) %>%
  distinct(Level_1, Paper_ID, Ranking_important) %>%
  group_by(Level_1, Ranking_important) %>%
  mutate(values_priority = length(unique(Paper_ID))) %>%
  distinct(Ranking_important,values_priority) 


values_priority_domain = df_crops_values %>%
  filter(!Ranking =="NA") %>%
    #filter(Ranking %in% c("most important", "important")) %>%
 # mutate(Ranking_important = recode(Ranking,
                                   #"most important" = "priority",
                                  # "important" = "priority")) %>%
  group_by(Domain) %>%
  mutate(Nbr_value = length(Level_1)) %>%
  distinct(Domain, Nbr_value)
  
# 104 citations of values for D2, 

# Important domain of values within the paper ranked as priority / important
values_priority_domain_2 = df_crops_values %>%
  filter(!Ranking =="NA") %>%
    filter(Ranking %in% c("most important", "important")) %>%
 mutate(Ranking_important = recode(Ranking,
                                   "most important" = "priority",
                                   "important" = "priority")) %>%
  group_by(Domain) %>%
  mutate(Nbr_value = length(Level_1)) %>%
  distinct(Domain, Nbr_value)

57*100/89 # 64% of values of Domain 2 (Cultural preferences) were ranked as priority

```

## Values associated with specific crops 

```{r Values specific crops , include=FALSE,echo=FALSE}

rice_values = df_crops_values %>%
  filter(Crop_name == "Oryza sativa") %>%
  group_by(Level_1) %>%
  mutate(Rice_values_L1 = length(Level_1)) %>%
  distinct(Level_1,Rice_values_L1)


Crop_value_cultural_pref_domain = df_crops_values %>%
  filter(Domain == "2. Cultural preferences") %>%
  group_by(Crop_name) %>%
  mutate(Crop_number = length(Crop_name)) %>%
    filter(Crop_name == "Manihot esculenta") 
  
  
cassava_value = df_crops_values %>%
  filter(Crop_name == "Manihot esculenta") %>%
  group_by(Level_1) %>%
  mutate(Rice_values_L1 = length(Level_1)) %>%
  distinct(Level_1,Rice_values_L1) %>%
  mutate(Per_Rice_values_L1 = Rice_values_L1*100/136)


```


# Co-occurence network of values 

## Building dataset: crop level

```{r dataset network , include=FALSE,echo=FALSE}

# Meand and SD number of values per studies
df_values_occurence_number = df_crops_values %>%
  select(Paper_ID, Level_1) %>%
  group_by(Paper_ID) %>%
  mutate(Nbr_value= length(Level_1)) %>%
  distinct(Paper_ID,Nbr_value )
mean(df_values_occurence_number$Nbr_value)
sd(df_values_occurence_number$Nbr_value)

## Number of domain per paper 
df_values_occurence_number = df_crops_values %>%
    mutate(Level_1_domain_number = str_extract(Level_2, "^\\d+") %>% paste0(".")) %>%
  group_by(Paper_ID) %>%
  mutate(Nbr_Domain = length(unique(Level_1_domain_number))) %>%
  distinct(Paper_ID, Nbr_Domain)
12*100/125 # 10% of rerported a single domain 


# Creating the network
df_values_occurence = df_crops_values %>%
  distinct(Code_U, Level_1) %>%
  mutate(Occurence = 1) %>%
    pivot_wider(names_from = Code_U, values_from = Occurence,values_fill = 0)

mat_values_occurence = as.matrix(df_values_occurence)
namesmat=mat_values_occurence[,1]
mat_values_occurence=mat_values_occurence[,-1]

mat_values_occurence=apply(mat_values_occurence, MARGIN = 2, FUN = as.numeric)

row.names(mat_values_occurence)=namesmat

ordering <- sort(rownames(mat_values_occurence))


# Cumpting the p-value and alpha for each co-occurence of values per article
df_occurence_value <- affinity(data = mat_values_occurence[ordering,], row.or.col = "row", squarematrix = c("all")) 


# Filtering significant association of values 

df_values_occurence_subset = df_occurence_value$all %>%
  select(entity_1, entity_2,obs_cooccur_X,p_value,alpha_mle) %>%
  mutate(p_value = as.numeric(p_value),
         p_value = format(p_value, scientific = FALSE),
         alpha_mle=as.numeric(alpha_mle)) %>%
   filter(p_value<=0.05 & alpha_mle > 0) %>%
  mutate(values_A_Domain = str_extract(entity_1, "\\d") %>%
  paste0("."),
         values_B_Domain = str_extract(entity_2, "\\d") %>%
  paste0("."),
         values_A_number = str_extract(entity_1, "^\\d+(?:\\.\\d+)?(?=\\.)") %>%
  paste0("."),
   values_B_number = str_extract(entity_2, "^\\d+(?:\\.\\d+)?(?=\\.)") %>%
  paste0(".")) 

```

## Degree centrality: crop level

```{r values network centrality , include=FALSE,echo=FALSE}

df_nodes = df_values_occurence_subset %>%
  select(entity_1,entity_2) %>%
  pivot_longer(c(1:2)) %>%
  distinct(value) %>%
  rename(Level_1 = value) %>%
  left_join(df_tree_values , "Level_1") %>%
  distinct(Level_1, .keep_all=T) %>%
  mutate(Domain = str_extract(Level_1, "\\d") %>%
  paste0("."),
         Level_1_number = str_extract(Level_1, "^\\d+(?:\\.\\d+)?(?=\\.)") %>%
  paste0(".")) %>%
  select(Level_1_number,Domain, Level_1)

net <- graph_from_data_frame(d=df_values_occurence_subset[,8:9], vertices=df_nodes, directed = F)

values_degree = degree(net) %>% as.data.frame()


# Drawing Fig. S2

pal.nodes = c("#506F80", "#456234", "#F06666","#B05726",  "#C6B3D7", "#FEC990")
              
              

vertexCol <- igraph::vertex_attr(net, "Domain")

vertexCol[vertexCol == "1."] = pal.nodes
vertexCol[vertexCol == "2."] = pal.nodes[2]
vertexCol[vertexCol == "3."] = pal.nodes[3] 
vertexCol[vertexCol == "4."] = pal.nodes[5]
vertexCol[vertexCol == "5."] = pal.nodes[4]
vertexCol[vertexCol == "6."] = pal.nodes[6]

plot(net, vertex.color=vertexCol, 
     edge.size=8, vertex.size = degree(net),
     edge.color = "black", vertex.label.color="black",
     vertex.label.dist=-1,asp=1, rescale=T)

```



## Chord diagram showing the co-occurence of values (Fig.3)


```{r chord diagram , include=FALSE,echo=FALSE}

df_values_occurence_domain = df_values_occurence_subset %>%
  select(entity_1, entity_2, obs_cooccur_X) %>%
  mutate(entity_1_number = str_extract(entity_1, "^\\d+") %>% paste0("."),
         entity_2_number = str_extract(entity_2, "^\\d+") %>% paste0("."),
         entity_3 = paste0(entity_1_number, "_",entity_2_number ),
         N_total_occ = sum(obs_cooccur_X)) %>%
  select(entity_3,obs_cooccur_X, N_total_occ) %>%
  group_by(entity_3) %>%
  mutate(Nbr_domain_occ = sum(obs_cooccur_X)) %>%
  distinct(entity_3,Nbr_domain_occ,N_total_occ)
151*100/628 # 24% 

print("Within the Agroecological traits domain , about a quarter of co-occurrences (24%) involved values within the same domain ")

### Chord diagram: level of domain

df_values_occurence_domain = df_values_occurence_subset %>%
  select(entity_1, entity_2, obs_cooccur_X) %>%
  mutate(entity_1_number = str_extract(entity_1, "^\\d+") %>% paste0("."),
         entity_2_number = str_extract(entity_2, "^\\d+") %>% paste0("."),
         N_total_occ = sum(obs_cooccur_X)) %>%
  group_by(entity_1_number,entity_2_number) %>%
  mutate(Nbr_domain_occ = sum(obs_cooccur_X)) %>%
  distinct(entity_1_number,entity_2_number,Nbr_domain_occ,N_total_occ) %>%
  select(-N_total_occ)

chordDiagram(df_values_occurence_domain, annotationTrack = c("grid", "name"))


```


# Values and integration to market (subsistance vs global market)


```{r integration to market , include=FALSE,echo=FALSE}

df_market_integration = df_articles %>%
  select(Paper_ID, integration_to_market_recode) 


## Mean number of values per type of market integration

df_crops_values_market = df_crops_values %>%
    full_join(df_market_integration, "Paper_ID") %>%
  drop_na(integration_to_market_recode) %>%
  group_by(Paper_ID) %>%
  mutate(Nbr_values = length(Level_1)) %>%
  distinct(Paper_ID,Nbr_values,integration_to_market_recode) %>%
  group_by(integration_to_market_recode) %>%
  mutate(Mean_value = mean(Nbr_values),
         SD_value = sd(Nbr_values)) %>%
  distinct(integration_to_market_recode,Mean_value,SD_value)

# Domain level 
df_crops_values_market_d = df_crops_values %>%
    full_join(df_market_integration, "Paper_ID") %>%
  drop_na(integration_to_market_recode) %>%
  group_by(integration_to_market_recode) %>%
  mutate(Nbr_value_T = length(Domain)) %>%
  group_by(Domain,integration_to_market_recode) %>%
  mutate(Nbr_value_d = length(Domain),
         Per_value_d = Nbr_value_d*100/Nbr_value_T) %>%
  distinct(integration_to_market_recode, Domain, Nbr_value_T,Nbr_value_d, Per_value_d )

# level 1 
df_crops_values_market_l = df_crops_values %>%
    full_join(df_market_integration, "Paper_ID") %>%
  drop_na(integration_to_market_recode) %>%
  group_by(Level_1,integration_to_market_recode) %>%
  mutate(Nbr_value_l = length(Level_1)) %>%
  distinct(integration_to_market_recode, Level_1, Nbr_value_l)

# level 2
df_crops_values_market_l2 = df_crops_values %>%
    full_join(df_market_integration, "Paper_ID") %>%
  drop_na(integration_to_market_recode) %>%
  group_by(Level_2,integration_to_market_recode) %>%
  mutate(Nbr_value_l = length(Level_2)) %>%
  distinct(integration_to_market_recode, Level_2, Nbr_value_l)

```


# Values and type of crops (perennial vs annual)

```{r crop types , include=FALSE,echo=FALSE}

## Perennial vs annual (% of values reported)

type_crops_values = df_crops_values %>%
  mutate(Nbr_values = length(Level_1)) %>%
  group_by(Crop_type) %>%
  mutate(Nbr_values_crop = length(Level_1)*100/Nbr_values ) %>%
  distinct(Nbr_values_crop,Nbr_values)

# level domain and level 2
type_crops_values_detail = df_crops_values %>%
    group_by(Crop_type, Domain) %>%
  mutate(Nbr_values_crop = length(Domain )) %>%
  group_by(Crop_type, Domain,Level_1) %>%
    mutate(Nbr_values_crop_2 = length(Level_1 )) %>%
  distinct(Crop_type,Level_1,Domain, Nbr_values_crop,Nbr_values_crop_2)


# Level 2
type_crops_values_detail_2 = df_crops_values %>%
    group_by(Crop_type, Level_2) %>%
  mutate(Nbr_values_crop = length(Level_2 )) %>%
  distinct(Crop_type,Level_2,Nbr_values_crop)
```

# Values and crop uses (food vs non-food crops)

```{r crop use , include=FALSE,echo=FALSE}

### number of species

food_crop = df_crops_values %>%
  filter(!food_crops %in% c("NR", "NA")) %>%
  group_by(food_crops) %>%
  mutate(Nb_crop = length(unique(Crop_name))) %>%
  distinct(food_crops,Nb_crop)
 
# Level domain 
usage_crops_values_domain = df_crops_values %>%
    filter(!food_crops %in% c("NR", "NA")) %>%
  drop_na(food_crops) %>%
    group_by(food_crops) %>%
  mutate(Nbr_value_D = length(Domain)) %>%
  group_by(food_crops, Domain) %>%
  mutate(Nbr_values = length(Domain )*100/Nbr_value_D ) %>%
  distinct(food_crops,Domain, Nbr_values)



```


# Values and crop role (staple vs cash crops)
```{r crop role , include=FALSE,echo=FALSE}

### number of species 

Role_crops_number = df_crops_values %>%
  filter(Crop_role_2 %in% c("cash", "staple")) %>%
  group_by(Crop_role_2) %>%
  mutate(Nbr_crops = length(unique(Crop_name))) %>%
  distinct(Crop_role_2,Nbr_crops) %>%
  mutate(Nbr_crops_T = 135,
         Per_crops = Nbr_crops*100/Nbr_crops_T)

# Level domain 
role_crops_values_domain = df_crops_values %>%
    group_by(Crop_role_2) %>%
  mutate(Nbr_value_D = length(Domain)) %>%
  group_by(Crop_role_2, Domain) %>%
  mutate(Nbr_values = length(Domain )*100/Nbr_value_D ) %>%
  distinct(Crop_role_2,Domain, Nbr_values)

# Level 1
role_crops_values= df_crops_values %>%
  mutate(Nbr_values = length(Level_1)) %>%
  group_by(Crop_role_2) %>%
  mutate(Nbr_values = length(Nbr_values)*100/Nbr_values ) %>%
  distinct(Crop_role_2,Nbr_values)



role_crops_values_2_level_1 = df_crops_values %>%
    group_by(Crop_role_2,Domain) %>%
  mutate(Nbr_value_D = length(Level_1)) %>%
  group_by(Crop_role_2, Level_1) %>%
  mutate(Nbr_values = length(Level_1 )) %>%
  distinct(Crop_role_2,Level_1,Domain, Nbr_value_D,Nbr_values)
```


# Values within agroecosystems

```{r agroecosystem , include=FALSE,echo=FALSE}

# Number of studies 

df_agroecosystem_nb_studies = df_crops_values %>%
  filter(Crop_level == "agroecosystem") %>%
  mutate(Nbr_studies = length(unique(Paper_ID)),
         Per_studies = Nbr_studies*100/125) %>%
  distinct(Crop_level,Nbr_studies,Per_studies)



df_agroecosystem = df_crops_values %>%
  filter(Crop_level == "agroecosystem") %>%
  group_by(Domain) %>%
  mutate(Nbr_values = length(Domain)) %>%
    group_by(Domain, Level_1) %>%
    mutate(Nbr_values_l = length(Level_1)) %>%
  distinct(Domain,Nbr_values, Level_1,Nbr_values_l )

```



# Modelisation (negative binomial glm)

```{r models , include=FALSE,echo=FALSE}

## df coders ### 

df_coders = df_articles %>%
  distinct(Paper_ID, coder)

## Models df ##
df_models = df_models %>%
  left_join(df_coders, "Paper_ID") %>%
  mutate(main_topic = as.factor(main_topic),
         coder = as.factor(coder),
         value_centred = as.factor(value_centred), 
         rsch_area_gnl = as.factor(rsch_area_gnl),
         Nbr_thinnest_value = as.numeric(Nbr_thinnest_value),
         Nbr_valued_crops = as.numeric(Nbr_valued_crops)) 

hist(df_models$Nbr_thinnest_value)
colSums(is.na(df_models))

### Coders effect ###

mod <- lm(Nbr_thinnest_value ~ Nbr_valued_crops * coder, data = df_models)
summary(mod)


### Model 1: glm 

m1 = glm(Nbr_thinnest_value ~  Nbr_valued_crops + 
                     main_topic + value_centred + rsch_area_gnl ,
                 data=df_models, family = "poisson")

summary(m1)

#### Check for models output

testDispersion(m1)
simulationOutput <- simulateResiduals(fittedModel = m1, plot = F)
plot(simulationOutput)

print("Overdispertion of the residuals => negative binomial glm")


#### Model 2: negative binomial glm


m2 = glm.nb(Nbr_thinnest_value ~   scale(Nbr_valued_crops) + 
                    relevel(main_topic, ref="practice adopt_aband") +
              relevel(value_centred, ref="No") + 
              relevel(rsch_area_gnl, ref="Social sciences"),
                 data=df_models)

summary(m2)
car::Anova(m2, type=2) # because the data is unbalanced
testDispersion(m2) 
simulationOutput_m2 <- simulateResiduals(fittedModel = m2, plot = F)
plot(simulationOutput_m2) 

# Confidence interval
confint(m2)



## Drawing the plots 


#### Estimate et CI ####

df_mod_values <- broom.mixed::tidy(m2, conf.int = TRUE, effects = c("fixed", "ran_pars"))

Variable_name <- data.frame(
  term = rep(c("A", "B", "C"), 1),
  estimate = rep(0, 1),
  std.error = rep(0, 1),
  statistic = rep(0, 1),
  p.value = rep(0, 1),
  conf.low = rep(0, 1),
  conf.high = rep(0, 1)
)

df_mod_values = rbind(df_mod_values,Variable_name)

df_mod_final_betas = df_mod_values %>%
  filter(!term %in% c("(Intercept)","sd__(Intercept)", "sd__Observation" )) %>%
  mutate(Variable = recode(term,
                           "scale(Nbr_valued_crops)" = "Number of valued crops",
                             "relevel(main_topic, ref = \"practice adopt_aband\")climate change and adatation" = "Climate change and adaptation", 
                             "relevel(main_topic, ref = \"practice adopt_aband\")drivers of crop choices" = "Drivers of crop choices",
                             "relevel(main_topic, ref = \"practice adopt_aband\")local crop or diversity" = "Local crop or diversity", 
                             "relevel(main_topic, ref = \"practice adopt_aband\")participatory breeding & crop adoption" = "Participatory breeding & crop adoption",
                             "relevel(value_centred, ref = \"No\")Yes" = "Yes", 
                             "relevel(rsch_area_gnl, ref = \"Social sciences\")Agriculture sc. & tech." = "Agriculture sc. & tech.",
                             "relevel(rsch_area_gnl, ref = \"Social sciences\")Environment & ecology" = "Environment & ecology",
                           "A" = "Main topic (base: Adoption or abandonment of practices)",
                           "B" = "Values centred (base: No)",
                           "C" = "Research area (base: Social Sciences)"
                           ),
         p.value_round = round(p.value, 2),
         Color_significance = case_when(p.value_round <= 0.05 ~ "Significant", TRUE  ~ "No_ignificant"))


# Ordering the variables
df_mod_final_betas$Order_type_variable = factor(df_mod_final_betas$Variable,
                                                levels=rev(c("Number of valued crops",
                                                             "Main topic (base: Adoption or abandonment of practices)",
                                                             "Climate change and adaptation",
                                                             "Drivers of crop choices",
                                                             "Local crop or diversity",
                                                             "Participatory breeding & crop adoption",
                                                             "Values centred (base: No)",
                                                             "Yes",
                                                             "Research area (base: Social Sciences)",
                                                             "Agriculture sc. & tech.",
                                                             "Environment & ecology")))


ggplot(df_mod_final_betas, aes(x = estimate, y = Order_type_variable, colour=Color_significance)) +
  geom_vline(xintercept = 0, color = "black") +
  geom_point(size = 2.3) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0, size = 0.8) +
  theme_bw() +
  theme(legend.position = "none") +
  xlab("Standardized regression coefficient") +
  ylab("")  + theme(panel.grid.major = element_blank(), # remove the major lines
                                                                                             panel.grid.minor = element_blank(),
                                                                                             panel.spacing.x = unit(1.1, "lines"),
                                                                                             strip.background.y = element_blank(),
                                                                                             strip.text.y = element_blank(),
                                                                                             strip.background.x = element_rect(colour="black", fill="white", 
                                                                                                                               size=1, linetype="solid"),
                                                                                             strip.text.x = element_text(size=10),
                                                                                             strip.placement = "outside") + 
  scale_color_manual(values=c("gray80", "black"))

print("The figure was edited using Inkscape to improve its visual quality")

```

# Academic field and values

```{r values research area , include=FALSE,echo=FALSE}

Research_Area = df_articles %>%
  select(Paper_ID,Rsch_area_gnl )


Research_area_Value = df_crops_values %>%
  full_join(Research_Area, "Paper_ID") %>%
  group_by(Rsch_area_gnl) %>%
  mutate(Nbr_vlue_T = length(Paper_ID)) %>%
  group_by(Rsch_area_gnl, Domain) %>%
  mutate(Nbr_value_Domain = length(Paper_ID)/Nbr_vlue_T,
         Per_value_Domain = length(Paper_ID)*100/Nbr_vlue_T) %>%
  distinct(Rsch_area_gnl, Nbr_vlue_T,Nbr_value_Domain,Per_value_Domain)

color_domain <-  c("#506F80", "#456234", "#F06666","#B05726",  "#C6B3D7", "#FEC990") ; names(color_domain) <- c("1. Social and symbolic",
                                                                                                   "2. Cultural preferences",
                                                                                                   "3. Socio-economic",
                                                                                                   "5. Maintenance of options",
                                                                                                   "6. Agroecological traits",
                                                                                                   "4. Ecological interactions")

color_domain <- alpha(color_domain, 0.7)

Research_area_Value$Order_type = factor(Research_area_Value$Domain, levels=c("1. Social and symbolic","2. Cultural preferences",
                                                                         "3. Socio-economic","4. Ecological interactions","5. Maintenance of options","6. Agroecological traits" ))

ggplot(Research_area_Value, aes(fill=Order_type, y=Nbr_value_Domain, x=Rsch_area_gnl)) + 
    geom_bar(position="stack", stat="identity")+ scale_fill_manual(values=color_domain) + theme_bw() + 
  xlab("Research areas") + ylab("Proportion of values (%)") + scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels=c("Agriculture sc. & tech. \n (n= 1,036) ", "Environment & ecology \n (n= 505)", "Social sciences \n (n= 175)")) + 
  guides(fill=guide_legend(title="Domains:")) + theme_bw() + theme(panel.grid.major = element_blank(), # remove the major lines
                                                          panel.grid.minor = element_blank(),
                                                          legend.position = "right",
                                                          strip.text.y = element_blank(),
                                                          strip.background.x = element_rect(colour="black", fill="white", 
                                                                                            size=1, linetype="solid"),
                                                          strip.text.x = element_text(size=10),
                                                          strip.placement = "outside")


## Exact's fisher test

fischer_t = df_crops_values %>%
  full_join(Research_Area, "Paper_ID") %>%
  group_by(Rsch_area_gnl) %>%
  mutate(Nbr_vlue_T = length(Paper_ID)) %>%
  group_by(Rsch_area_gnl, Domain) %>%
  mutate(Nbr_value_Domain = length(Paper_ID)/Nbr_vlue_T)


dput(unique(Research_Area$Rsch_area_gnl))
contingency_table <- table(fischer_t$Rsch_area_gnl, fischer_t$Domain)
contingency_table

PropLig=prop.table(contingency_table,margin=1)
PropLig


fisher.test(contingency_table,hybrid = TRUE)


```



# Drivers of crops change 

```{r Drivers , include=FALSE,echo=FALSE}

# Percent of studies 

df_drivers_full1 = df_drivers %>%
  filter(!Drivers == "NA") 
length(unique(df_drivers_full1$Paper_ID))
99*100/125 

# Proportion of drivers 
df_drivers_full <- df_drivers %>%
  filter(!Drivers == "NA") %>%
  group_by(Drivers) %>%
  mutate(freq = length(unique(Paper_ID))) %>%
  filter(!freq == 1 ) %>%
  mutate(sum = 99) %>% 
  mutate(percent= freq*100/sum) %>%
  as.data.frame() %>%
  droplevels() %>% 
  distinct(Drivers, percent) 


ggplot(df_drivers_full, aes(reorder(x= Drivers, -percent), y=percent )) +
  geom_bar(stat="identity", fill="black") + coord_flip() + theme_bw() + theme(panel.grid.major = element_blank(), # remove the major lines
                                                   panel.grid.minor = element_blank(),
                                                   legend.position = "none") + 
  xlab("") + ylab("Proportion of articles (%)")
```


